---
title: "Prolific"
author: "Nicole Wagner"
output: html_document
date: "2026-02-09"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Libraries

```{r}
library(dplyr)
library(lme4)
library(lmerTest)
library(readr)
library(ggplot2)
library(tidyr)
library(tibble)
library(readxl)
library(broom.mixed)
library(emmeans)
library(broom)
library(broom.mixed)
library(purrr)
library(stringr)
```

---

# reading in files
```{r}
# masterfile previously calculated with all viral marker, immune markers, raw values, normalized values and delta and log fold change values
master_file <- read.csv("/Users/nicole.wagner/Library/CloudStorage/OneDrive-KarolinskaInstitutet/Documents/Folders_to_transfer_to_KI_laptop/paxlovid_2026/My_stuff/March_2026_files/master_file_outcome_nano_olink.csv")


```

# First: Viral biology

	
## definig the log transformed viral markers
```{r}
viral_markers <- c(
  "nano_Envelope_nano_log2",
  "nano_ORF3a_nano_log2",
  "nano_Nucleocapsid_nano_log2",
  "nano_ORF7a_nano_log2",
  "nano_ORF1ab_nano_log2",
  "nano_SARS_CoV_2_orf1ab_REV_nano_log2",
  "nano_Spike_nano_log2"
 # "nano_FYN_nano_log2"
)
```

## pivoting to the current format 
```{r}

viral_long <- master_file %>%
  mutate(treatment_group = trtgrp,
          time_num = as.numeric(visit),
          time_factor = factor(visit,
                         levels = c(1,16,45,90),
                         labels = c("d1","d16","d45","d90"))) %>%
  filter(visit %in% c(1,16,45)) %>%
  dplyr::select(subject_id, treatment_group, time_num, time_factor,
         all_of(viral_markers)) %>%
  pivot_longer(
    cols = all_of(viral_markers),
    names_to = "gene",
    values_to = "viral_value"
  ) %>%
  filter(!is.na(viral_value))
  
  
 
```



## baseline balance /// at baseline we note no significant difference between the two groups (old run)
```{r}
baseline_df <- viral_long %>%
  filter(time_factor == "d1")

baseline_tests <- baseline_df %>%
  group_by(gene) %>%
  do(tidy(t.test(viral_value ~ treatment_group, data = .)))
```



## looking at the interaction terms
 pvalues and estimates

interaction interpretation:
For each gene:
	•	interaction p < 0.05 → treatment changes viral trajectory over time
	•	estimate < 0 → faster decline under treatment
	•	estimate > 0 → slower decline under treatment



## baseline adjusted sensitivity model
 The interaction terms indicate an additional decrease in viral load at both day 16 and day 45 in the Paxlovid group relative to placebo.

```{r}
baseline_vals <- viral_long %>%
  filter(time_factor == "d1") %>%
  select(subject_id, gene, baseline_val = viral_value)

viral_adj <- viral_long %>%
  left_join(baseline_vals, by = c("subject_id","gene"))

baseline_adjusted_viral_model <- lmer(
  viral_value ~ baseline_val + time_factor * treatment_group + (1 | subject_id),
  data = viral_adj
)
```
## A forest plot for the interaction term

```{r}



# Placebo as reference; baseline/screening timepoint as reference
viral_adj_2 <- viral_adj %>%
  mutate(
    treatment_group = factor(treatment_group, levels = c("Placebo", "Paxlovid")),
    time_factor = factor(time_factor, levels = c("d1", "d16", "d45"))  
  )


# FIT MODELS PER MARKER/Gene

models <- viral_adj_2 %>%
  group_by(gene) %>%  
  group_map(.keep = TRUE, ~ {
    dat <- .x
    # lmer will drop rows with NAs in any used variable automatically, but being explicit:
    dat <- dat %>% filter(!is.na(viral_value), !is.na(time_factor), !is.na(treatment_group))

    m <- lmer(viral_value ~ baseline_val + time_factor * treatment_group + (1 | subject_id),
              data = dat, REML = TRUE)
    list(gene = unique(dat$gene), model = m)
  })

# element name list
models_named <- setNames(lapply(models, `[[`, "model"),
                         vapply(models, function(x) as.character(x$gene), character(1)))

# interaction terms
res <- imap_dfr(models_named, ~{
  broom.mixed::tidy(.x, effects = "fixed", conf.int = TRUE) %>%
    mutate(gene = .y)
}) %>%
  filter(str_detect(term, "^time_factor.*:treatment_groupPaxlovid$")) %>%
  mutate(
    timepoint = str_match(term, "^time_factor(.*):treatment_groupPaxlovid$")[,2],
    # nice labels
    timepoint = recode(timepoint, "d16" = "Day 16", "d45" = "Day 45",
                       .default = timepoint),
    effect_label = paste0(gene, " — ", timepoint)
  )

#  multiple-testing correction across all extracted tests
res <- res %>%
  mutate(p_adj = p.adjust(p.value, method = "BH"))



res <- res %>%
  arrange(p_adj, estimate) %>%
  mutate(effect_label = factor(effect_label, levels = rev(unique(effect_label))))


```


## facet by timepoint
```{r}
res2 <- res %>%
  mutate(gene = factor(gene, levels = rev(unique(gene)))) %>%
  mutate(gene_clean = stringr::str_extract(gene, "(?<=nano_).*?(?=_nano)"))

res2 <- res2 %>%
  mutate(sig = p.value < 0.05)   # or p_adj < 0.05

p <- ggplot(res2, aes(x = estimate, y = gene_clean)) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high), height = 0.2) +
  geom_point(aes(color = sig), size = 2) +
  geom_text(
    aes(
      label = sprintf("p=%.3f", p.value),
      x = conf.high + 0.02
    ),
    size = 3,
    hjust = 0
  ) +
  facet_wrap(~timepoint, scales = "free_y") +
  theme_bw() +
  labs(
    x = "Interaction effect (Paxlovid vs Placebo at timepoint)",
    y = NULL
  ) +
  scale_color_manual(
    values = c("FALSE" = "black", "TRUE" = "red"),
    guide = "none"
  )

p
```


# second: Clinical Outcomes


## first set up and define the outcomes

```{r}


lower_better <- c("fss_score","mfs_score","cat","mmrc",
                  "nijmegen_score","compass_31_total","maps")

higher_better <- c("x6mwt_of_predicted","grip_str_of_predicted",
                   "steps_per_day_scaled","n_sit_to_stand","stepping_time",
                   "moca")

all_outcomes <- c(lower_better, higher_better)
delta_cols <- paste0("delta_", all_outcomes)
```

```{r}
master_file <- master_file %>%
  mutate(
    steps_per_day_scaled = as.numeric(scale(steps_per_day))
  )


steps_delta <- master_file %>%
  select(subject_id, visit, steps_per_day_scaled) %>%
  group_by(subject_id) %>%
  arrange(visit, .by_group=TRUE) %>%
  mutate(
    baseline_steps_scaled = steps_per_day_scaled[visit == 1][1],
    delta_steps_per_day_scaled =
      steps_per_day_scaled - baseline_steps_scaled
  ) %>%
  ungroup() %>%
  select(subject_id, visit, delta_steps_per_day_scaled)

master_file <- master_file %>%
  left_join(
    steps_delta,
    by = c("subject_id","visit")
  ) 
```


## prepping the clinicial data

```{r}
df_clin2 <- master_file %>%
  rename(treatment_group = trtgrp) %>%
  mutate(
    treatment_group = factor(treatment_group,
                             levels = c("Placebo","Paxlovid")),
    visit = as.integer(visit),
    time_factor = factor(
      visit,
      levels = c(1,16,45,90),
      labels = c("d1","d16","d45","d90")
    )
  )
```

## long table and direction alignment
```{r}
long_delta <- df_clin2 %>%
  select(subject_id, treatment_group, visit, time_factor,
         all_of(all_outcomes), all_of(delta_cols)) %>%
  pivot_longer(
    cols = all_of(c(all_outcomes, delta_cols)),
    names_to = "variable",
    values_to = "value"
  )

long_delta <- long_delta %>%
  mutate(
    is_delta = str_starts(variable, "delta_"),
    outcome = str_remove(variable, "^delta_")
  )

long_delta <- long_delta %>%
  mutate(
    value_type = if_else(is_delta, "delta", "value")
  ) %>%
  select(-variable) %>%
  pivot_wider(
    names_from = value_type,
    values_from = value
  )

long_delta <- long_delta %>%
  mutate(
    delta_improve = case_when(
      outcome %in% lower_better ~ -delta,
      outcome %in% higher_better ~ delta,
      TRUE ~ NA_real_
    )
  )
```

## checking timepoints that have an outcomes (if outcome was measured at that time)
```{r}
timepoint_map <- long_delta %>%
  filter(!is.na(delta_improve)) %>%
  group_by(outcome) %>%
  summarise(
    timepoints = paste(sort(unique(time_factor)), collapse = ", "),
    n_timepoints = n_distinct(time_factor),
    .groups="drop"
  )

#write.csv(timepoint_map,"outcome_measurement_timepoint_map.csv")
timepoint_map
```

## missingness filter (keeping outcomes that have enough subject per arm for at least one timepoint followup)

```{r}
min_n_per_arm_time <- 10

keep_outcomes <- long_delta %>%
  filter(!is.na(delta_improve), time_factor != "d1") %>%
  
  # count per arm
  group_by(outcome, time_factor, treatment_group) %>%
  summarise(n = n_distinct(subject_id), .groups = "drop") %>%
  
  # get min per arm
  group_by(outcome, time_factor) %>%
  summarise(min_arm_n = min(n), .groups = "drop") %>%
  
  #  now operate ONLY on observed timepoints
  group_by(outcome) %>%
  summarise(
    n_timepoints = n(),  # how many timepoints exist for this outcome
    all_ok = all(min_arm_n >= min_n_per_arm_time),
    .groups = "drop"
  ) %>%
  
  filter(all_ok) %>%
  pull(outcome)

long_delta_filt <- long_delta %>%
  filter(outcome %in% keep_outcomes,
         !is.na(delta_improve),
         time_factor != "d1")
```

## model per outcome (to handle all oucomes including ones with missing timepoint such as moca which has only two timepoints)


```{r}
baseline_df <- long_delta %>%
  filter(time_factor == "d1") %>%
  select(subject_id, outcome, baseline_value = value)

long_value <- long_delta %>%
  left_join(baseline_df, by = c("subject_id", "outcome"))

long_value_filt <- long_value %>%
  filter(outcome %in% keep_outcomes,
         time_factor != "d1",
         !is.na(value),
         !is.na(baseline_value))
```
```{r}
timepoint_counts <- long_value_filt %>%
  distinct(outcome, time_factor) %>%
  count(outcome, name = "n_timepoints")

long_value_filt2 <- long_value_filt %>%
  left_join(timepoint_counts, by = "outcome")
```


```{r}
fit_one <- function(df_one) {
  n_tp <- dplyr::n_distinct(df_one$time_factor)

  if (n_tp == 1) {
    lm(
      value ~ treatment_group + baseline_value,
      data = df_one
    )
  } else {
    lmer(
      value ~ time_factor * treatment_group +
        baseline_value +
        (1 | subject_id),
      data = df_one,
      REML = TRUE
    )
  }
}

models <- long_value_filt2 %>%
  group_by(outcome) %>%
  group_split() %>%
  set_names(map_chr(., ~ unique(.x$outcome))) %>%
  map(fit_one)
```

## extract treatment effects at each timepoint
```{r}


extract_one <- function(model, outcome_name, df_one) {
  n_tp <- dplyr::n_distinct(df_one$time_factor)

  if (n_tp == 1) {
    broom::tidy(model, conf.int = TRUE) %>%
      filter(term == "treatment_groupPaxlovid") %>%
      transmute(
        outcome = outcome_name,
        timepoint = as.character(unique(df_one$time_factor)),
        contrast = "Paxlovid - Placebo",
        estimate = estimate,
        std.error = std.error,
        statistic = statistic,
        p.value = p.value,
        conf.low = conf.low,
        conf.high = conf.high
      )
  } else {
    emmeans(model, ~ treatment_group | time_factor) %>%
      contrast(method = "revpairwise") %>%   # gives Paxlovid - Placebo
      summary(infer = TRUE) %>%
      as.data.frame() %>%
      transmute(
        outcome = outcome_name,
        timepoint = as.character(time_factor),
        contrast = contrast,
        estimate = estimate,
        std.error = SE,
        statistic = t.ratio,
        p.value = p.value,
        conf.low = lower.CL,
        conf.high = upper.CL
      )
  }
}
```


```{r}
models_input <- long_value_filt %>%
  group_by(outcome) %>%
  group_split() %>%
  set_names(map_chr(., ~ unique(.x$outcome)))

results <- map_df(models_input, function(df_one) {
  outcome_name <- unique(df_one$outcome)
  model <- fit_one(df_one)
  extract_one(model, outcome_name, df_one)
})
results <- results %>%
  mutate(p_adj = p.adjust(p.value, method = "BH"))
```

## forest plot

	
	•	CI crossing 0 → not statistically supported
	•	BH-adjusted p < 0.05 → multiple-testing robust
	•	estimate > 0 → Paxlovid showed more improvement than placebo
	•	estimate < 0 → Paxlovid showed less improvement / worse change than placebo


```{r}

forest_df <- results %>%
  mutate(
    timepoint = factor(timepoint, levels = c("d16", "d45", "d90")),

    estimate_harmonized = case_when(
      outcome %in% lower_better ~ -estimate,
      outcome %in% higher_better ~ estimate,
      TRUE ~ estimate
    ),
    conf.low.harmonized = case_when(
      outcome %in% lower_better ~ -conf.high,
      outcome %in% higher_better ~ conf.low,
      TRUE ~ conf.low
    ),
    conf.high.harmonized = case_when(
      outcome %in% lower_better ~ -conf.low,
      outcome %in% higher_better ~ conf.high,
      TRUE ~ conf.high
    ),

    effect_dir = if_else(
      estimate_harmonized > 0,
      "Paxlovid more improvement",
      "Paxlovid less improvement"
    ),

    label = paste(outcome, timepoint, sep = " — ")
  ) %>%
  arrange(outcome, timepoint) %>%
  mutate(label = factor(label, levels = label))


p <- ggplot(forest_df,
       aes(x = estimate_harmonized, y = label, color = effect_dir)) +
  geom_point(size = 2.5) +
  geom_errorbarh(aes(xmin = conf.low.harmonized, xmax = conf.high.harmonized),
                 height = 0.2,
                 color = "black") +
  geom_vline(xintercept = 0, linetype = "dashed") +
  scale_color_manual(values = c(
    "Paxlovid more improvement" = "blue",
    "Paxlovid less improvement" = "orange"
  )) +
  labs(
    x = "Treatment effect on improvement from baseline",
    y = "",
    color = "",
    title = "Treatment Effects on Continuous Secondary Outcomes by Timepoint"
  ) +
  theme_bw()
p
```

### eqvas table details

```{r}
eqvas_table <- df_clin2 %>%
  filter(!is.na(eqvas)) %>%
  group_by(treatment_group, visit) %>%
  summarise(
    n = n(),
    mean = mean(eqvas, na.rm = TRUE),
    sd = sd(eqvas, na.rm = TRUE),
    .groups = "drop"
  )

eqvas_table_wide <- eqvas_table %>%
  mutate(mean_sd = sprintf("%d, %.1f ± %.1f", n, mean, sd)) %>%
  select(visit, treatment_group, mean_sd) %>%
  pivot_wider(
    names_from = treatment_group,
    values_from = mean_sd
  )

#write.csv(eqvas_table_wide,"eqvas_table_wide.csv")

```

### eqvas analysis alone 16
```{r}
eqvas_df <- df_clin2 %>%
  select(subject_id, treatment_group, visit, eqvas) %>%
  filter(visit %in% c(1, 16)) %>%
  pivot_wider(
    names_from = visit,
    values_from = eqvas,
    names_prefix = "d"
  ) %>%
  rename(
    eqvas_d1 = d1,
    eqvas_d16 = d16
  ) %>%
  filter(!is.na(eqvas_d1), !is.na(eqvas_d16))

model_eqvas <- lm(
  eqvas_d16 ~ treatment_group + eqvas_d1,
  data = eqvas_df
)

library(broom)

res_eqvas_16 <- tidy(model_eqvas, conf.int = TRUE) %>%
  filter(term == "treatment_groupPaxlovid")
```


# now defining a responder threshold for the outcomes

## definining threshold and groups

```{r}

lower_better <- c("fss_score","mfs_score","cat","mmrc",
                  "nijmegen_score","compass_31_total","maps")

higher_better <- c("steps_per_day_scaled","stepping_time","n_sit_to_stand",
                   "x6mwt_of_predicted","eqvas","moca")

all_outcomes <- c(lower_better, higher_better)
```


## extracting baseline values
```{r}
baseline_df <- master_file %>%
  filter(visit == 1) %>%
  select(subject_id, all_of(all_outcomes)) %>%
  pivot_longer(
    cols = all_of(all_outcomes),
    names_to = "outcome",
    values_to = "baseline_val"
  )
```

## build delta table and baseline joined
```{r}
delta_cols <- paste0("delta_", all_outcomes)

delta_long <- master_file %>%
  rename(treatment_group = trtgrp) %>%
  mutate(
    treatment_group = factor(treatment_group,
                             levels = c("Placebo","Paxlovid")),
    visit = as.integer(visit)) %>%
  select(subject_id, visit, treatment_group, all_of(delta_cols)) %>%
  pivot_longer(
    cols = all_of(delta_cols),
    names_to = "outcome",
    values_to = "delta",
    names_prefix = "delta_"
  )

resp_long <- delta_long %>%
  left_join(baseline_df, by = c("subject_id","outcome"))
```

## direction corrected improvement score

```{r}
resp_long <- resp_long %>%
  mutate(
    direction = case_when(
      outcome %in% higher_better ~  1,
      outcome %in% lower_better  ~ -1,
      TRUE ~ NA_real_
    ),
    improv = direction * delta
  )
```

## responder flag (75% + sensitivity)
```{r}
eps <- 1e-6

resp_long <- resp_long %>%
  mutate(
    base_abs = pmax(abs(baseline_val), eps),

    resp_75 = improv >= 0.75 * base_abs,
    resp_50 = improv >= 0.50 * base_abs,
    resp_90 = improv >= 0.90 * base_abs
  )
```

## sensitivity table
```{r}
resp_long %>%
  group_by(outcome, visit, treatment_group) %>%
  summarise(
    n = n(),
    resp_rate_75 = mean(resp_75, na.rm=TRUE),
    resp_rate_50 = mean(resp_50, na.rm=TRUE),
    resp_rate_90 = mean(resp_90, na.rm=TRUE)
  )

#write.csv(resp_long,"responder_table_sensitivity.csv")
```

## Responder analysis

```{r}

df0 <- master_file %>%
  rename(treatment_group = trtgrp)
```

```{r}
# 1) compute baseline mean/sd for steps
steps_ref <- df0 %>% filter(visit == 1) %>% summarise(mu = mean(steps_per_day, na.rm=TRUE),
                                                     sd = sd(steps_per_day, na.rm=TRUE))

mu_steps <- steps_ref$mu
sd_steps <- steps_ref$sd

# 2) scaled steps
df0 <- df0 %>%
  mutate(steps_per_day_scaled = (steps_per_day - mu_steps) / sd_steps)

# 3) baseline scaled steps per subject
steps_bl <- df0 %>%
  filter(visit == 1) %>%
  select(subject_id, steps_per_day_scaled_bl = steps_per_day_scaled)

# 4) delta scaled steps (current - baseline)
df0 <- df0 %>%
  left_join(steps_bl, by = "subject_id") %>%
  mutate(delta_steps_per_day_scaled = steps_per_day_scaled - steps_per_day_scaled_bl)
```

```{r}
lower_better <- c("fss_score","mfs_score","cat","mmrc",
                  "nijmegen_score","compass_31_total","maps")
higher_better <- c("x6mwt_of_predicted","grip_str_of_predicted",
                   "steps_per_day_scaled","n_sit_to_stand","stepping_time",
                   "eqvas","moca")

all_outcomes <- c(lower_better, higher_better)

delta_cols <- paste0("delta_", all_outcomes)

df_delta_long <- df0 %>%
  select(subject_id, visit, treatment_group, all_of(delta_cols)) %>%
  pivot_longer(
    cols = all_of(delta_cols),
    names_to = "outcome",
    values_to = "delta"
  ) %>%
  mutate(outcome = str_remove(outcome, "^delta_"))
```

```{r}
# baseline values in long form
df_baseline_long <- df0 %>%
  filter(visit == 1) %>%
  select(subject_id, all_of(all_outcomes)) %>%
  pivot_longer(cols = all_of(all_outcomes),
               names_to = "outcome",
               values_to = "baseline_val")

# join baseline onto deltas
df_resp_base <- df_delta_long %>%
  left_join(df_baseline_long, by = c("subject_id","outcome"))
```

```{r}
df_resp <- df_resp_base %>%
  mutate(
    direction = case_when(
      outcome %in% lower_better ~ "lower_better",
      outcome %in% higher_better ~ "higher_better",
      TRUE ~ NA_character_
    ),
    pct_change = ifelse(is.na(baseline_val) | baseline_val == 0, NA_real_,
                        delta / abs(baseline_val)),

    resp_50 = case_when(
      direction == "lower_better"  ~ as.integer(pct_change <= -0.50),
      direction == "higher_better" ~ as.integer(pct_change >=  0.50),
      TRUE ~ NA_integer_
    ),
    resp_75 = case_when(
      direction == "lower_better"  ~ as.integer(pct_change <= -0.75),
      direction == "higher_better" ~ as.integer(pct_change >=  0.75),
      TRUE ~ NA_integer_
    ),
    resp_90 = case_when(
      direction == "lower_better"  ~ as.integer(pct_change <= -0.90),
      direction == "higher_better" ~ as.integer(pct_change >=  0.90),
      TRUE ~ NA_integer_
    )
  )
```

## Fisher and Responder NNT
###removing baseline and NA
```{r}
resp_df <- df_resp %>%
  filter(visit != 1) %>%      # remove baseline
  filter(!is.na(resp_50))     # remove outcomes not measured at that visit
```

### reshaping for correct threshold
```{r}
resp_long <- resp_df %>%
  pivot_longer(
    cols = c(resp_50, resp_75, resp_90),
    names_to = "threshold",
    values_to = "responder"
  )
```

### responder rates
```{r}
resp_summary <- resp_long %>%
  group_by(outcome, visit, threshold, treatment_group) %>%
  summarise(
    responders = sum(responder == 1, na.rm = TRUE),
    n = n(),
    rate = responders / n,
    .groups = "drop"
  )

#write.csv(resp_summary,"responder_summary_rates.csv")

```



# risk difference

```{r}
calc_rd <- function(data, resp_col) {

  tab <- data %>%
    group_by(treatment_group) %>%
    summarise(
      n = n_distinct(subject_id),
      responders = sum(.data[[resp_col]] == 1, na.rm = TRUE),
      rate = responders / n,
      .groups = "drop"
    )

  if(nrow(tab) < 2) {
    return(tibble(
      pax_rate = NA,
      pbo_rate = NA,
      risk_diff = NA,
      p_value = NA
    ))
  }

  pax_rate <- tab$rate[tab$treatment_group == "Paxlovid"]
  pbo_rate <- tab$rate[tab$treatment_group == "Placebo"]

  rd <- pax_rate - pbo_rate

  mat <- table(data$treatment_group, data[[resp_col]])

  test <- tryCatch(
    fisher.test(mat),
    error = function(e) NULL
  )

  tibble(
    pax_rate = pax_rate,
    pbo_rate = pbo_rate,
    risk_diff = rd,
    p_value = ifelse(is.null(test), NA, test$p.value)
  )
}
```



```{r}
rd_75 <- df_resp %>%
  filter(!is.na(resp_75)) %>%
  group_by(outcome, visit) %>%
  group_modify(~ calc_rd(.x, "resp_75")) %>%
  ungroup()

rd_75 <- rd_75 %>%
  mutate(p_adj = p.adjust(p_value, method="BH"))

rd_75 <- rd_75 %>%
  mutate(nnt = ifelse(risk_diff > 0, 1/risk_diff, NA))

#write.csv(rd_75,"risk_difference_75percent.csv")

```

```{r}
rd_50 <- df_resp %>%
  filter(!is.na(resp_50)) %>%
  group_by(outcome, visit) %>%
  group_modify(~ calc_rd(.x, "resp_50")) %>%
  ungroup()

rd_50 <- rd_50 %>%
  mutate(p_adj = p.adjust(p_value, method="BH"))

rd_50 <- rd_50 %>%
  mutate(nnt = ifelse(risk_diff > 0, 1/risk_diff, NA))

rd_90 <- df_resp %>%
  filter(!is.na(resp_90)) %>%
  group_by(outcome, visit) %>%
  group_modify(~ calc_rd(.x, "resp_90")) %>%
  ungroup()

rd_90 <- rd_90 %>%
  mutate(p_adj = p.adjust(p_value, method="BH"))

rd_90 <- rd_90 %>%
  mutate(nnt = ifelse(risk_diff > 0, 1/risk_diff, NA))

#write.csv(rd_50,"risk_difference_50percent.csv")

#write.csv(rd_90,"risk_difference_90percent.csv")


```

```{r}

rd_75 <- rd_75 %>%
  filter(visit != 1)

p_75 <- ggplot(rd_75,
       aes(x = risk_diff,
           y = reorder(outcome, risk_diff),
           color = risk_diff > 0)) +
  geom_point(size = 2) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  facet_wrap(~visit) +
  scale_color_manual(values = c("firebrick","steelblue"),
                     labels = c("Placebo favored","Paxlovid favored"),
                     name = "Direction") +
  labs(
    title = "Risk Difference in ≥75% Responders",
    x = "Risk difference (Paxlovid − Placebo)",
    y = "Outcome"
  ) +
  theme_bw()

rd_90 <- rd_90 %>%
  filter(visit != 1)

p_90 <- ggplot(rd_90,
       aes(x = risk_diff,
           y = reorder(outcome, risk_diff),
           color = risk_diff > 0)) +
  geom_point(size = 2) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  facet_wrap(~visit) +
  scale_color_manual(values = c("firebrick","steelblue"),
                     labels = c("Placebo favored","Paxlovid favored"),
                     name = "Direction") +
  labs(
    title = "Risk Difference in ≥90% Responders",
    x = "Risk difference (Paxlovid − Placebo)",
    y = "Outcome"
  ) +
  theme_bw()


rd_50 <- rd_50 %>%
  filter(visit != 1)

p_50 <- ggplot(rd_50,
       aes(x = risk_diff,
           y = reorder(outcome, risk_diff),
           color = risk_diff > 0)) +
  geom_point(size = 2) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  facet_wrap(~visit) +
  scale_color_manual(values = c("firebrick","steelblue"),
                     labels = c("Placebo favored","Paxlovid favored"),
                     name = "Direction") +
  labs(
    title = "Risk Difference in ≥50% Responders",
    x = "Risk difference (Paxlovid − Placebo)",
    y = "Outcome"
  ) +
  theme_bw()
```

